Paper analysis

### 2025-03-26 Paper_analysis.Rmd
update site

>>>>

## N export base interactions

```{r nexpbase_int}
grid.arrange(
  int.nexpbase %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.nexpbase.ntr_pland %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

## N export margin interactions

```{r nexpmarg_int}
grid.arrange(
  int.nexpmarg %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.nexpmarg.ntr_pland %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

## Sediment export base interactions

```{r sedbase_int}
grid.arrange(
  int.sedexpbase %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.sedexpbase.ann_agr_ed %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

## Sediment export margin interactions

```{r sedmarg_int}
grid.arrange(
  int.sedexpmarg %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.sedexpmarg.ann_agr_ed %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

## Baseflow base interactions

```{r qbbase_int}
grid.arrange(
  int.qbbase %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.qbbase.field_frac_mn %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

## Baseflow margin interactions

```{r qbmarg_int}
grid.arrange(
  int.qbmarg %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.qbmarg.prn_agr_para_mn %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```
